From Education To Entrepreneurship

### 2014-11-29 FromEducationToEntrepreneurship.Rmd

### Research Interest

The process of allocating public funds for education is an opportunity to make calculated long-term investments in a nation's populace.  The rationale for decisions made during this process, however, is often difficult to understand.  For example, while many claims have been made in entrepreneurship literature regarding the importance of cultural and educational factors -- not just structural and economic factors -- in determining individual and societal tendencies to start a business, these factors are often not included in the decisionmaking process. As a matter of fact, only a few empirical studies have actually been carried out on this topic and most of them focused on which attitudes were favorable to starting a business, while almost none explored how cultural patterns affected these dispositions.

When cultural factors are examined, they are considered as a given feature that can hardly be traced. By having a closer look at education systems, however, we intend to explore the processes through which some of these cultural patterns are enhanced and passed from one generation to the next. Aside from parental education, schools are indeed the very place where children are taught how to fit into society. This research is an attempt to analyze  one trait in particular, self-confidence.

>>>>

### Policy Relevance

The process of allocating public funds for education is an opportunity to make calculated long-term investments in a nation's populace. The rationale for decisions made during this process, however, is often difficult to understand. That is, while many claims have been made in entrepreneurship literature regarding the importance of cultural and educational factors -- not just structural and economic factors -- in determining individual and societal tendencies to start a business, these factors are often not included in the decision-making process. Actually, only a few empirical studies have been carried out on this topic and most of them focused on which attitudes were favourable to starting a business, while almost none explored what determined these dispositions.
